Output Summary

### 2022-02-19 03-post-process/output-plots.Rmd
Update output plots to handle scaling/centering

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "size-based-surv"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: TRUE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

  # obtain posterior samples of total egg abundance scaled to WUL
  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
  E_scaled = (E/10000)/jags_data$wul[j]
  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Eggs/WUL")
mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
```

@@

@@

  # create vectors to predict survival at: for credible regions and mean curve
  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)

@@

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_seq)
    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
    pred_phi_Pa_Mb
  }

@@

@@

  # create vectors to predict survival at: for credible regions and mean curve
  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)

@@

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_seq)
    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
    pred_phi_Mb_Ma
  }

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "size-based-surv"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

  # obtain posterior samples of total egg abundance scaled to WUL
  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))

@@

xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, xlab)
mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
```

@@

  # obtain scaled/centered versions
  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
  L_Pb_star_lwr = (L_Pb_lwr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
  L_Pb_star_upr = (L_Pb_upr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]

@@

  # create vectors to predict survival at: for credible regions and mean curve
  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)

@@

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
    pred_phi_Pa_Mb
  }

@@

  # obtain scaled/centered versions
  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]

@@

  # create vectors to predict survival at: for credible regions and mean curve
  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)

@@

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
    pred_phi_Mb_Ma
  }
